Using reference models in feature selection \vspace{.1in}

### 2019-11-28 paper/ref_approach.tex
add a ref

\usepackage{amssymb,amsmath,amsthm}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{algorithm2e}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in feature selection problems},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\textwidth 6.0 true in
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Using reference models in feature selection problems 
	\vspace{.1in}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner and Aki Vehtari}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\textwidth]{graphics/correlation.pdf}
  \caption{Sample correlation plot of each feature (relevant in red, 
  non-relevant in blue) with the target variable $y$ and the latent variable 
  $f$ respectively on the x and y axis. Data are generated according to 
  procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
  $k=100$, $p=1000$.\\}
  \label{fig:correlation}
\end{figure}

@@

Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
the vertical axis and the average false discovery rate on the
horizontal axis based on 100 data simulations for the different
combinations of $n$ and $\rho$. The best selection performance is on the
top-left corner of each plot, as it implies the lowest false discovery
rate and the highest sensitivity. We see that regardless of the
applied selection method, the use of a reference model improves the
selection performance, as it reduces the false discovery rate (shifting
to the left) or increases the sensitivity (shifting upwards). In
accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
selection is. Thus, for easier selection scenarios, the benefits of
the reference model are smaller since the raw data already provide
enough information to identify the relevant covariates. The iterative
projection predictive approach has good false discovery rate in all cases, and the sensitivity is good except when the number of observations and the correlation level
are small. Tuning $\alpha$ might lead to improved selection, yet
the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
utility score for misspecified models with cross-validation \hl{(maybe add some references? The last sentence 
refers to the problem when comparing misspecified models using CV. Tuomas did a talk about this problem.
Maybe Aki can check the content and add some references - not sure Tuomas' work is already available)}.

@@

Relying on the idea of the reference model as a noise-filter, a
generic reference model approach, which can be used on top of any
feature selection procedure, consists of simply substituting the
target observations with corresponding point predictions of the
reference model, for instance, the posterior predictive
means. Afterwards, any method for feature selection can be used. We do
not argue that such a reference model approach should necessarily be
used as is for feature selection in real applications. There are
several more sophisticated reference model approaches available in the
literature \cite[see,
e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
which are likely to yield even better results. Rather, the reason for
focusing on this simple version is to enable a fair comparison between
a reference model and a purely data based approach when otherwise
using the same selection procedures. Other kinds of comparisons, as
the one presented in Section \ref{intro-example}, work well as
motivational examples but lack in terms of generality since the
presence or absence of a reference model is not the only aspect
differentiating the two procedures. We will come back to the more
general comparison in Section \ref{comparison}.

>>>>

\usepackage{amssymb,amsmath,amsthm}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{algorithm2e}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in feature selection},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\textwidth 6.0 true in
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Using reference models in feature selection 
	\vspace{.1in}}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner and Aki Vehtari}

@@

\begin{figure}[tp]
  \centering
  \vspace{-5mm}
  \includegraphics[width=0.4\textwidth]{graphics/correlation.pdf}
  \caption{Sample correlation plot of each feature (relevant in red, 
  non-relevant in blue) with the target variable $y$ and the latent variable 
  $f$ respectively on the x and y axis. Data are generated according to 
  procedure \eqref{eq:simulated_data} with parameters $n=70$, $\rho=0.3$,
  $k=100$, $p=1000$.\\}
  \label{fig:correlation}
\end{figure}

@@

Figure \ref{fig:sensitivity_vs_fdr_iterated} shows the average sensitivity on
the vertical axis and the average false discovery rate on the
horizontal axis based on 100 data simulations for the different
combinations of $n$ and $\rho$. The best selection performance is on the
top-left corner of each plot, as it implies the lowest false discovery
rate and the highest sensitivity. We see that regardless of the
applied selection method, the use of a reference model improves the
selection performance, as it reduces the false discovery rate (shifting
to the left) or increases the sensitivity (shifting upwards). In
accordance with what can be expected, the larger data set size ($n$) and the higher the true correlations ($\rho$), the easier the
selection is. Thus, for easier selection scenarios, the benefits of
the reference model are smaller since the raw data already provide
enough information to identify the relevant covariates. The iterative
projection predictive approach has good false discovery rate in all cases, and the sensitivity is good except when the number of observations and the correlation level
are small. Tuning $\alpha$ might lead to improved selection, yet
the main source of poor performance could well be the miscalibration of the uncertainty of the predictive
utility score for misspecified models with cross-validation \citep{bengio2004no}.

@@

Relying on the idea of the reference model as a noise-filter, a
generic reference model approach, which can be used on top of any
feature selection procedure, consists of simply substituting the
target observations with corresponding point predictions of the
reference model, for instance, the posterior predictive
means. Afterwards, any method for feature selection can be used. We do
not argue that such a reference model approach should necessarily be
used as is for feature selection in real applications. There are
several more sophisticated reference model approaches available in the
literature \cite[see,
e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
which are likely to yield even better results. Rather, the reason for
focusing on this simple version is to enable a fair comparison between
a reference model and a purely data based approach when otherwise
using the same selection procedures. Other kinds of comparisons, as
the one presented in Section \ref{intro-example}, work well as
motivational examples but lack in terms of generality since the
presence or absence of a reference model is not the only aspect
differentiating the two procedures.
% We will come back to the more
% general comparison in Section \ref{comparison}.
